### 2017-12-07 manuscript.rmd
fixed typos in code median_depth_contmap

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS

 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 densityMap(palpons_sim)
 dev.off()
```

@@

median_extended = cdata$Median.Depth.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label),]
depthmap_ext <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext)

>>>>

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 densityMap(palpons_sim)
 dev.off()
```

@@

median_extended = cdata$Depth.Median.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label)]
depthmap_ext <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext)
